Preferences interact: what consequences for a Schelling scenario?

### 2019-11-11 ethnic_value_rum.Rmd
updates check

---
output:
  bookdown::pdf_document2:
    toc: false
 #   keep_tex: false
    fig_caption: yes
title: "Preferences interact: what consequences for a Schelling scenario?"
# subtitle: "Target: BIGSSS Research Day"
author:  Rocco Paolillo, Andreas Flache, Jan Lorenz
date:  "`r  as.Date(Sys.time(), '%d %B %Y')`"
# "`r  as.Date(Sys.time(), '%d %B %Y')`"
language: en-GB
bibliography: "references.bib"
always_allow_html: yes
header-includes:
- \usepackage{float}
- \usepackage{multirow}
- \usepackage{xcolor} 
- \usepackage{amsmath}
- \usepackage{graphicx}

---

@@

# install.packages("tinytex", repos = "https://cloud.r-project.org" )

library(tidyverse)
library(ggplot2)
library(gridExtra)
library(tidyr)
library(plyr)
library(dplyr)

eq_10 <- read.csv("50_g_10_bh.csv",sep = ",",skip = 6)
names(eq_10) <- pull(read_csv("code_names.csv"))

mj_10 <- read.csv("80_g_10_bh.csv",sep = ",",skip = 6)
names(mj_10) <- pull(read_csv("code_names.csv"))

eq_30 <- read.csv("50_g_30_hb.csv", sep = ",", skip = 6)
names(eq_30) <- pull(read_csv("code_names.csv"))

mj_30 <- read.csv("80_g_30_bh.csv",sep = ",",skip = 6)
names(mj_30) <- pull(read_csv("code_names.csv"))

mj_30_10 <- read.csv("80_g_30_10.csv",sep = ",", skip = 6)
names(mj_30_10) <- pull(read_csv("code_names.csv"))

eq_30_10 <- read.csv("50_g_30_10.csv",sep = ",", skip = 6)
names(eq_30_10) <- pull(read_csv("code_names.csv"))

test <- read.csv("test-beta-eth.csv",sep = ",",skip = 6)
names(test)[names(test) == "X.step."] <- "step"
names(test)[names(test) == "X.run.number."] <- "run"
names(test)[names(test) == "beta.ie"] <- "beta_ie"
names(test)[names(test) == "mean..count..turtles.on.neighbors..with..ethnicity....ethnicity..of.myself...of.turtles.with..count..turtles.on.neighbors.....1."] <- "eth_seg"

raw_f <- rbind(eq_30,eq_10,mj_30,mj_10,eq_30_10,mj_30_10)

df_e_sqr <- raw_f$e_sqr - raw_f$v_sqr
df_v_crl <-  raw_f$v_crl - raw_f$e_crl

dataset <- cbind(raw_f,df_e_sqr,df_v_crl)

# check <- final[,c(9,10,27,11,12,28)]

write.csv(dataset, file = "dataset.csv",row.names=FALSE) # later for reproduction

@@

@@

```{r gg }

raw_f %>% filter(e_sqr == 30, v_crl == 10)

>>>>

---
output:
  bookdown::pdf_document2:
    toc: false
 #   keep_tex: false
    fig_caption: yes
title: "Preferences interact: what consequences for a Schelling scenario?"
# subtitle: "Target: BIGSSS Research Day"
author:  Rocco Paolillo, Andreas Flache, Jan Lorenz
# date:  "`r  as.Date(Sys.time(), '%d %B %Y')`"
# "`r  as.Date(Sys.time(), '%d %B %Y')`"
language: en-GB
bibliography: "references.bib"
always_allow_html: yes
header-includes:
- \usepackage{float}
- \usepackage{multirow}
- \usepackage{xcolor} 
- \usepackage{amsmath}
- \usepackage{graphicx}
---

@@

# install.packages("tinytex", repos = "https://cloud.r-project.org" )
library(tidyverse)
library(ggplot2)
library(gridExtra)
library(tidyr)
library(plyr)
library(dplyr)

@@

To explore what levels of $\beta$ should not be excluded from the manipulations, I built a specific model with a unique beta for ethnic composition ($\beta_{ie}$ ) that does not change among agents. At each run I incremented degree of $\beta_{ie} \in[0,100]$ and let run for 1000 ticks with agents asynchronously relocating (not 1 agent for 1 tick, all to complete the procedure to restart). In each condition linear function was used: the preference peak of agents was $100\%$ for ethnically similar

To explore what levels of $\beta$ should not be excluded from the manipulations, I made a specific model "rum_eth.nlogo" (in material), with a unique $\beta$ for all agents. I run the simulation for 1000 ticks (not 1 agent 1 tick):
* linear function: peak preference for all agents at $100 \%$
* density == $70 \%$
* equal distribution of value orientation in each ethnic group
* changing $beta_ie$ at each run $beta_ie \in[0,100]$

```{r one-beta, fig.cap="Comparison of ethnic segregation for one beta-ethnic, not interaction. Used one-beta.csv from simulation rum-eth.nlogo" , include=TRUE}

a <- read.csv("one-beta.csv",sep = ",",skip = 6)
names(a)[names(a) == "mean..count..turtles.on.neighbors..with..ethnicity....ethnicity..of.myself....count..turtles.on.neighbors....of.turtles.with..count..turtles.on.neighbors.....1." ] <- "eth_seg"

a %>% filter(ticks == 0  | ticks == 500  | ticks == 100 | ticks == 1000)  %>%  filter(beta.ie >= 0 & beta.ie <= 15) %>% ggplot(aes(x = beta.ie, y = eth_seg)) + geom_bar(stat="identity") + facet_wrap(~ ticks, labeller = label_both)

@@
